Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-03-30 talk/icooolps2011/paper.tex
a minimal abstract

XXX

>>>>

A meta-tracing JIT is a JIT that is applicable to a variety of different
languages without explicitly encoding language semantics into the compiler. So
far, meta-tracing JITs lacked a way to feed back runtime information into the
compiler, which restricted their performance. In this paper we describe the
mechanisms in PyPy's meta-tracing JIT that can be used to control runtime
feedback in flexible and language-specific ways. These mechanisms are flexible
enough to implement classical VM techniques such as maps and polymorphic inline
caches.
